---
title: "Homework 4 Federalist Papers"
author: "Khan"
date: "5/1/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The purpose of this homework is to use clustering analysis to determine if Hamilton or Madison wrote the disputed Federalist Paper. Kevin Hager and I worked collaboratively on this homework. The code is also referencing  from class material. 
## Load R Packages

Install required R packages:

```{r}
#install.packages('RWeka')
#install.packages('tidyverse')  # data manipulation
#install.packages('cluster')    # clustering algorithms
#install.packages('factoextra') # clustering algorithms & visualization
#install.packages('gridExtra')
```

```{r}
require(RWeka)
require(tidyverse)  # data manipulation
require(cluster)    # clustering algorithms
require(factoextra) # clustering algorithms & visualization
require(gridExtra)  # subfigure layout package
```

## Data Preparation

Setup the working environment and load the papers.csv file

```{r}
papers <- read.csv("/Users/gozi/Downloads/fedPapers85.csv") ### <-- specify correct data location
str(papers)


```

To remove any missing value that might be present in the data, type this:

```{r}
papers <- na.omit(papers)
```

Remove the label information and replace the row names with abbreviated authors

```{r}

papers_unlabeled <- papers[,c(3:72)]

authors <- rep(NA,85)
for (a in 1:85){
  authors[a] <- paste(substr(papers$author[a],1,2),a)
}

rownames(papers_unlabeled) <- authors
head(papers_unlabeled)
```

Scaling the data 
```{r}
papers_unlabeled <- scale(papers_unlabeled)
head(papers_unlabeled)

typeof(papers_unlabeled)
```

```{r}
distance <- get_dist(papers_unlabeled)
fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
```


## KMeans Clustering 


```{r}
model_r = kmeans(papers_unlabeled, centers = 7, nstart = 25)
model_r
```

print the centroids

```{r}
model_r$centers
```

get cluster assignment

```{r}
cluster_assignment <- data.frame(papers,model_r$cluster)
#View(cluster_assignment)
```


View results using fviz_cluster.

```{r}
fviz_cluster(model_r, data = papers_unlabeled)
```

## Select the best K


```{r}
k3 <- kmeans(papers_unlabeled, centers = 3, nstart = 25)
k4 <- kmeans(papers_unlabeled, centers = 4, nstart = 25)
k5 <- kmeans(papers_unlabeled, centers = 5, nstart = 25)

# plots to compare
p1 <- fviz_cluster(k3, geom = "point",  data = papers_unlabeled) + ggtitle("k = 3")
p2 <- fviz_cluster(k4, geom = "point",  data = papers_unlabeled) + ggtitle("k = 4")
p3 <- fviz_cluster(k5, geom = "point",  data = papers_unlabeled) + ggtitle("k = 5")
p4 <- fviz_cluster(model_r, geom = "point", data = papers_unlabeled) + ggtitle("k = 7")

require(gridExtra)
grid.arrange(p1, p2, p3, p4, nrow = 2)
```

Based on these plots it is safe to resonable to assume the Maddison wrote the disputed papers. We will now use HAC to show if there is a difference

```{r}
d <- dist(papers_unlabeled, method = "euclidean")

# Hierarchical clustering using Complete Linkage
hc1 <- hclust(d, method = "complete" )

# Plot the obtained dendrogram
plot(hc1, cex = 0.6, hang = -1)
```
```{r}
# Dissimilarity matrix, remember hclust need a matrix input
d <- dist(papers_unlabeled, method = "euclidean")

# Ward's method
hc5 <- hclust(d, method = "ward.D2" )

# Cut tree into 4 groups
cluster_label <- cutree(hc5, k = 3)

# Number of members in each cluster
table(cluster_label)
```

```{r}
iris_clustered <- cbind(papers, cluster_label)

```


```{r}
plot(hc5, cex = 0.6)
rect.hclust(hc5, k = 3, border = 2:5)
```
Based on this dendrogram, the disputed papers fall into the cluster with Madison, so therefore it can be assumed Madison wrote the papers. 
